%A concise statement of the system definition, including the key features, both functional and non-functional

%\begin{itemize}
  %\item Private Satellite Network
   %\item Routing on the network using constraints
    %\item Supervisors
    %\item Briefcase
    %\item Integration with other systems
%\end{itemize}

Our proposed solution is a device that has similar appearance to a contemporary smartphone that provides navigation instructions to the courier. These instructions are provided via an interface built on top of Google Maps \cite{GoogleMaps}, to enhance the usability of the system. For the duration of a delivery, a courier is linked to a \textit{supervisor} who is situated in a predetermined control room. The courier and supervisor are able to communicate throughout the duration of the delivery through a text messaging interface on the courier’s device and a supervisor frontend desktop environment on the controller’s desktop computer.

As well as monitoring and communicating with the courier, the supervisor is also responsible for ensuring that the courier takes a safe and efficient route to their destination. This can be achieved by adding \textit{constraints} to the delivery. A constraint can include an area that the courier is not allowed to travel within, as well the methods of transport that the courier is allowed to use. When a constraint is added to a delivery, the system will re-route the courier's route to satisfy the constraints.

One unique aspect of the system is that will run on a private satellite network which encrypts all transferred data. This maximises overall system security as a potential hacker will firstly need to obtain customised hardware and break through our encryption system to gain access to the network. Furthermore, the use of satellites improves the availability of the system; a courier will still be able to transmit and receive to the network in more remote locations compared to a more conventional approach (e.g. using a mobile phone network).

Our second unique selling point is the physically reinforced briefcase that a courier can use during the delivery. This briefcase is electronically locked and can only be unlocked with a message that has been encrypted a private key supplied by the recipient. To unlock the briefcase, one must place the encrypted message on a USB memory stick and insert it into a concealed USB port on the briefcase. Before a delivery commences, the customer will have the option of whether they would like the briefcase to destroy the items enclosed within it. In case of this option being chosen, the briefcase will destroy its contents if the courier presses the concealed panic button.

The way customers will pay for the transfer of their mission-critical item is through a base system purchase and then they will choose which of our add-ons to include. The base purchase will include the private network, the use of our couriers to deliver their item within the UK and the transport/accommodation for the courier. The add-ons would include the use of our briefcases with the electronic locking mechanism, transfers to Europe and global transfers. 
